Correlations between gender and research topics at three major archaeology conferences

### 2023-09-04 analysis/paper/paper.Rmd
update figures after acceptance at JFA

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dpi = 300
)
```

@@

# how many papers per conf?
ggplot(all_conf_tbl) +
  aes(conf,
      fill = gender) +
  geom_bar(position = "dodge") +
  # colours from https://blog.datawrapper.de/gendercolor/
  scale_fill_discrete(type = c("#8625F5", "#1FC3AA")) +
  theme_minimal(base_size = 14) +
  theme(legend.position = c(.2,.60)) +
  labs(x = "", 
       y = "number of papers presented in 2018")
```

@@

@@

SAA18_stm_plot$plot
ggplot2::ggsave(here::here("analysis/figures/SAA18_stm_plot.png"), 
       height = 7, 
       width = 6)

@@

EAA18_stm_plot$plot
ggsave(here::here("analysis/figures/EAA18_stm_plot.png"), height = 7, width = 6)

>>>>

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dpi = 600
)

@@

# how many papers per conf?
ggplot(all_conf_tbl) +
  aes(conf,
      fill = gender) +
  geom_bar(position = "dodge") +
  # colours from https://blog.datawrapper.de/gendercolor/
  scale_fill_discrete(type = c("#8625F5", "#1FC3AA")) +
  theme_minimal(base_size = 14) +
  theme(legend.position = c(.2,.60)) +
  labs(x = "", 
       y = "number of papers presented in 2018")

ggplot2::ggsave(here::here("analysis/figures/fig_1_basic_info_papers_per_conf.tiff"), 
       height = 4, 
       width = 6,
       dpi = 600,
       bg = "white")
```

@@

# https://www.tandfonline.com/action/authorSubmission?show=instructions&journalCode=yjfa20
he = 4.5
wi = 7
dpi = 800
plot_file_format <-  "tiff"

@@

SAA18_stm_plot$plot
ggplot2::ggsave(here::here(paste0("analysis/figures/fig_2_SAA18_stm_plot.",
                                  plot_file_format)), 
       height = he, 
       width = wi,
       dpi = dpi)

@@

EAA18_stm_plot$plot
ggsave(here::here(paste0("analysis/figures/fig_3_EAA18_stm_plot.", 
                  plot_file_format)),
       height = he, 
       width = wi,
       dpi = dpi)
